### 2023-06-22 manuscript.tex
local styles [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/b1393612506612279d1adce2c9bc387fde40c48f.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/b1393612506612279d1adce2c9bc387fde40c48f/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5340383730

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/e60f158440d0393345a67a362a123fa00df7f8e1/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/e60f158440d0393345a67a362a123fa00df7f8e1}{stain/2022-fdo-paper@e60f158}
on June 22, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/b1393612506612279d1adce2c9bc387fde40c48f/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/b1393612506612279d1adce2c9bc387fde40c48f}{stain/2022-fdo-paper@b139361}
on June 22, 2023.
